---
title: "group project CIS 690"
author: "Tsion Sherbeza"
date: "2023-05-30"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(dplyr)
library(ggplot2)
data <- read.csv("patients.csv")
head(data)
# Calculate summary statistics
summary(data[, 1:8])
# Calculate summary statistics
summary_stats <- data.frame(
  Mean = colMeans(data[, 1:8]),
  Median = sapply(data[, 1:8], median),
  Standard_Deviation = sapply(data[, 1:8], sd),
  Q1 = sapply(data[, 1:8], quantile, probs = 0.25),
  Q2 = sapply(data[, 1:8], quantile, probs = 0.5),
  Q3 = sapply(data[, 1:8], quantile, probs = 0.75)
)

# Print the summary statistics
print(summary_stats)

```

```{r}
library(ggplot2)

# Visualization 1: Histogram of Glucose levels
ggplot(data, aes(x = Glucose)) +
  geom_histogram(binwidth = 5, fill = "lightblue") +
  labs(title = "Distribution of Glucose Levels", x = "Glucose", y = "Frequency")

# Visualization 2: Boxplot of BMI by Diagnosis
ggplot(data, aes(x = Diagnosis, y = BMI)) +
  geom_boxplot(fill = "lightgreen", color = "black") +
  labs(title = "BMI by Diagnosis", x = "Diagnosis", y = "BMI")

# Visualization 3: Scatter plot of Age and BloodPressure
ggplot(data, aes(x = Age, y = BloodPressure)) +
  geom_point(color = "darkblue") +
  labs(title = "Age vs. Blood Pressure", x = "Age", y = "Blood Pressure")

# Visualization 4: Bar plot of the number of Pregnancies
ggplot(data, aes(x = Pregnancies, fill = Diagnosis)) +
  geom_bar(position = "dodge") +
  labs(title = "Number of Pregnancies by Diagnosis", x = "Number of Pregnancies", y = "Count")

# Visualization 5: Violin plot of Insulin levels by Diagnosis
ggplot(data, aes(x = Diagnosis, y = Insulin)) +
  geom_violin(fill = "lightpink", color = "black") +
  labs(title = "Insulin Levels by Diagnosis", x = "Diagnosis", y = "Insulin")
```

***Explanation***
The histogram of glucose levels reveals the overall distribution of glucose measurements, which can help determine if there are specific ranges associated with gestational diabetes.
The boxplot of BMI by Diagnosis shows the median, quartiles, and potential outliers for BMI, allowing for a comparison between patients with and without gestational diabetes.
The scatter plot of age and blood pressure provides insights into any potential relationship between these variables and can help identify any patterns or trends.
The bar plot of the number of pregnancies helps determine if there is an association between the number of pregnancies and the diagnosis of gestational diabetes.


```{r}
# Find missing values
missing_values <- apply(data == 0, 2, sum)

# Replace missing values with medians
for (i in 1:length(missing_values)) {
  if (missing_values[i] > 0) {
    data[data[, i] == 0, i] <- median(data[, i], na.rm = TRUE)
  }
}
# Calculate the IQR for each variable
iqr_values <- apply(data[, 1:8], 2, IQR)

# Find outliers using the IQR rule
outliers <- sapply(data[, 1:8], function(x) {
  lower <- quantile(x, 0.25) - 1.5 * iqr_values[length(iqr_values)]
  upper <- quantile(x, 0.75) + 1.5 * iqr_values[length(iqr_values)]
  x < lower | x > upper
})
```
```{r}
# Calculate the IQR for each variable
iqr_values <- apply(data[, 1:8], 2, IQR)

# Replace outliers with the nearest non-outlying values within a certain range (Winsorization)
for (i in 1:ncol(data)) {
  lower <- quantile(data[, i], 0.25) - 1.5 * IQR(data[, i])
  upper <- quantile(data[, i], 0.75) + 1.5 * IQR(data[, i])
  data[data[, i] < lower, i] <- lower
  data[data[, i] > upper, i] <- upper
}
print(data)
```
```{r}
# Set the CRAN mirror
chooseCRANmirror(graphics=FALSE, ind=1)

# Install and load the necessary library
install.packages("ggcorrplot")
library(ggcorrplot)

# Calculate the correlation matrix
cor_matrix <- cor(data[, 1:8])

# Create a correlogram
ggcorrplot(cor_matrix, type = "upper", lab = TRUE)

```

```{r}
install.packages("caret")

# Standardize the features
standardized_data <- scale(data[, 1:8])
# Select the best features and create the logistic regression model
library(caret)

# Create a logistic regression model
LRM1 <- glm(Diagnosis ~ Glucose + BMI + Age, data = data, family = binomial)

# Predict the outcome using LRM1
predictions <- predict(LRM1, data, type = "response")

# Convert data$Diagnosis to factor with levels
data$Diagnosis <- factor(data$Diagnosis, levels = c(0, 1))

# Convert predicted values to factor with levels
predictions <- factor(ifelse(predictions >= 0.5, 1, 0), levels = c(0, 1))

# Create a classification report
classification_report <- caret::confusionMatrix(predictions, data$Diagnosis)
print(classification_report)


```


***Explanation***
: In the context of the classification report, precision indicates the ability of the model to correctly identify pregnant women with gestational diabetes. Higher precision values indicate a lower rate of false positives.In the context of the classification report, recall indicates the ability of the model to correctly capture and identify all pregnant women who have gestational diabetes. Higher recall values indicate a lower rate of false negatives.The F1 score considers both false positives and false negatives and provides a comprehensive measure of the model's overall performance. Higher F1 scores indicate better overall performance.In the classification report, it indicates the count of instances for each class (diabetes and non-diabetes). It helps to understand the distribution of the actual data and the number of instances used for evaluation.

```{r}
# Calculate the accuracy score
accuracy <- sum(predictions == data$Diagnosis) / length(predictions)
print(accuracy)
```
***Explanation***
The resulting accuracy score represents the percentage of correct predictions made by the logistic regression model. It provides an overall measure of the model's performance in classifying gestational diabetes cases correctly. Higher accuracy scores indicate better performance, as they reflect a higher proportion of correct predictions compared to the total number of instances.

By executing this code, you will obtain the accuracy score of the logistic regression model. It quantifies the model's ability to accurately predict the diagnosis of gestational diabetes, providing a single metric to assess the model's overall performance.

```{r}
# Create LRM2 using all independent features
LRM2 <- glm(Diagnosis ~ ., data = data, family = binomial)
# View the summary of LRM2
summary(LRM2)

```


```{r}
library(caret)

# Create a logistic regression model (LRM1) with the best features
LRM1 <- glm(Diagnosis ~ Glucose + BMI + Age, data = data, family = binomial)

# Create a logistic regression model (LRM2) with all features
LRM2 <- glm(Diagnosis ~ ., data = data, family = binomial)

# Predict the outcome using LRM1 and LRM2
predictions_LRM1 <- ifelse(predict(LRM1, data, type = "response") >= 0.5, 1, 0)
predictions_LRM2 <- ifelse(predict(LRM2, data, type = "response") >= 0.5, 1, 0)

# Convert actual values and predicted values to factors with the same levels
actual_values <- factor(data$Diagnosis, levels = c(0, 1))
predictions_LRM1 <- factor(predictions_LRM1, levels = c(0, 1))
predictions_LRM2 <- factor(predictions_LRM2, levels = c(0, 1))

# Create classification reports
classification_report_LRM1 <- caret::confusionMatrix(predictions_LRM1, actual_values)
classification_report_LRM2 <- caret::confusionMatrix(predictions_LRM2, actual_values)

# Compare accuracy scores
accuracy_LRM1 <- classification_report_LRM1$overall['Accuracy']
accuracy_LRM2 <- classification_report_LRM2$overall['Accuracy']

print(paste("Accuracy Score (LRM1):", accuracy_LRM1))
print(paste("Accuracy Score (LRM2):", accuracy_LRM2))

# Compare classification reports
print("Classification Report (LRM1):")
print(classification_report_LRM1)
print("Classification Report (LRM2):")
print(classification_report_LRM2)

```



