---
title: "Project"
author: "Srinath"
date: "2023-05-29"
output: word_document
---

## Import Project Packages
```{r}
# Import libraries
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(pheatmap)
library(zoo)
```

## Load CSV Data File
```{r}
# Load data 
patient.data <- read.csv("C:\\Users\\rdede\\Downloads\\patients.csv")

# Show first few rows
head(patient.data)

# Show statistical summary
summary(patient.data)
```

## Data Dimensions
```{r}
## Data dimension before deleting duplicates
dim(patient.data)

## Data dimension after deleting duplicates
Unique.data<-unique(patient.data)
dim(Unique.data)
```

## Dependent Value Data Distribution
```{r}
## Show distribution of target variable in pie chart
ggplot(Unique.data, aes(x = "", fill = factor(Diagnosis))) +
  geom_bar(width = 1) +
  coord_polar(theta = "y") +
  labs(fill = "Diagnosis") +
  ggtitle("Diagnosis Distribution") +
  theme_void()
```

## Adressing Unbalanced Dependent Value
Five features that contains 0 values (which are equal to missing values) that is about the same amount as that is needed to get the target value balanced. Since False (0) values for Diagnosis are over represented, False (0) values are removed where there are missing values for the variables Glucose, BloodPressure, SkinThickness, Insulin, and BMI. This way, the big skewness to 0 is removed for these variables, and is the target value more balanced to contain a equal amount of True and False Diagnosis.
```{r}
#Since data distribution of target variable is not even, followed downsizing of Diagnosis "0" underlined data 
# Subset the rows with Diagnosis value of 0
no.diabetes.data <- patient.data[patient.data$Diagnosis == 0, ]

# Check for 0 values in specified columns and remove the rows
no.diabetes.filtered.data <- no.diabetes.data[!(no.diabetes.data$Glucose == 0 | no.diabetes.data$BloodPressure == 0 | no.diabetes.data$SkinThickness == 0 | no.diabetes.data$Insulin == 0 | no.diabetes.data$BMI == 0), ]

# Combine the filtered rows with the remaining rows that have Diagnosis value not equal to 0
balanced.patient.data <- rbind(no.diabetes.filtered.data, patient.data[patient.data$Diagnosis != 0, ])

# Reset row names
row.names(balanced.patient.data) <- NULL

# Show first few rows of data frame
head(balanced.patient.data)
```

## Dependent Value Data Distribution After Balancing
```{r}
# Show distribution of target variable post balancing in pie chart
ggplot(balanced.patient.data, aes(x = "", fill = factor(Diagnosis))) +
  geom_bar(width = 1) +
  coord_polar(theta = "y") +
  labs(fill = "Diagnosis") +
  ggtitle("Diagnosis Distribution") +
  theme_void()
```

## Visualize Statistical Summary of the Dataset
```{r}
#EDA Visualization
##Box Plot
independent.variables <- balanced.patient.data[, 1:8]
long.data <- pivot_longer(independent.variables, everything(), names_to = "variable", values_to = "value")
ggplot(long.data, aes(x = variable, y = value)) +
  geom_boxplot() +
  xlab("") +
  ylab("Value") +
  theme_minimal()
```

## Visualize Distributions of the Dataset
```{r}
##Histogram
Pregnancies <- ggplot(balanced.patient.data, aes(x = Pregnancies)) + geom_histogram() + ggtitle("Pregnancies")
Glucose <- ggplot(balanced.patient.data, aes(x = Glucose)) + geom_histogram() + ggtitle("Glucose")
BloodPressure <- ggplot(balanced.patient.data, aes(x = BloodPressure)) + geom_histogram() + ggtitle("Blood Pressure")
SkinThickness <- ggplot(balanced.patient.data, aes(x = SkinThickness)) + geom_histogram() + ggtitle("Skin Thickness")
Insulin <- ggplot(balanced.patient.data, aes(x = Insulin)) + geom_histogram() + ggtitle("Insulin")
BMI <- ggplot(balanced.patient.data, aes(x = BMI)) + geom_histogram() + ggtitle("BMI")
Pedigree <- ggplot(balanced.patient.data, aes(x = Pedigree)) + geom_histogram() + ggtitle("Pedigree")
Age <- ggplot(balanced.patient.data, aes(x = Age)) + geom_histogram() + ggtitle("Age")
grid.arrange(
  Pregnancies, Glucose, BloodPressure, SkinThickness,
  Insulin, BMI, Pedigree, Age,
  nrow = 3
)

```


## Replacing Missing Values
```{r}

cleaned.patient.data <- balanced.patient.data

# All zeros for the independent variables were said to be as NAs hence can be replaced with Medians
for (i in 2:8) {
  cleaned.patient.data[, i] <- ifelse(balanced.patient.data[, i] == 0, median(balanced.patient.data[balanced.patient.data[, i] != 0, i], na.rm = TRUE), balanced.patient.data[, i])
}

# Show first few rows to see if 0's were replaced by median of the column
head(cleaned.patient.data)
```

## Removing Outliers 
```{r}
# Create a capping function
treating_outliers <- function(x) {
  qntls <- quantile(x, probs = c(0.25, 0.75))
  iqr <- qntls[2] - qntls[1]
  lb <- qntls[1] - 1.5 * iqr
  ub <- qntls[2] + 1.5 * iqr
  x[x < lb] <- lb
  x[x > ub] <- ub
  return(x)
}

# Apply capping function on independent variables
cleaned.patient.data[, 1:8] <- apply(cleaned.patient.data[, 1:8], 2, treating_outliers)


# Show new statistical summary through boxplot
cleaned.independent.variables <- cleaned.patient.data[, 1:8]
long_data <- pivot_longer(cleaned.independent.variables, everything(), names_to = "variable", values_to = "value")
ggplot(long_data, aes(x = variable, y = value)) +
  geom_boxplot() +
  xlab("") +
  ylab("Value") +
  theme_minimal()

```
```{r}
#test check the normality
variables <- c("Pregnancies", "Glucose", "BloodPressure", "SkinThickness", "Insulin", "BMI", "Pedigree", "Age")

# Loop through variables
for (variable in variables) {
  # Perform Shapiro-Wilk test for normality
  shapiro_test <- shapiro.test(cleaned.patient.data[[variable]])
  
  # Print variable name and test results
  cat("Variable:", variable, "\n")
  cat("Shapiro-Wilk test statistic (W):", shapiro_test$statistic, "\n")
  cat("Shapiro-Wilk test p-value:", shapiro_test$p.value, "\n")
  cat("\n")
}

```

```{r}
##check summary post data cleaning
summary(cleaned.independent.variables)
```


```{r}
##Correlation Matrix
#check correlation post data cleaning
correlation.mtrx <- cor(cleaned.patient.data)
correlation.percentages <- round(correlation.mtrx * 100, 2)
pheatmap(correlation.percentages,
         main = "Correlation Matrix (%)",
         fontsize = 10,
         fontsize_row = 8,
         fontsize_col = 8,
         color = colorRampPalette(c("navy", "white", "firebrick3"))(100),
         show_rownames = TRUE,
         show_colnames = TRUE,
         display_numbers = TRUE,
         number_color = "black",
         number_format = "%.2f%%")

```

``` {r}
write.csv(cleaned.patient.data, "C:\\Users\\rdede\\Documents\\MNSU - master\\Semester 2 - Summer 2023\\Group Assignment\\Cleaned_patients.csv", row.names=FALSE)
```